---
title: "MTA Fare"
author: "JW"
date: "7/17/2017"
output: 
  ioslides_presentation: 
    widescreen: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# zoom out the markdown file
# Run Presentation, for shiny App, click the app, load in a new browser, 
# refresh or click the time line tab

```

## NYC MTA introduction

New York City Matropolitom Transport Aurhority (MTA) and overall information

- One of the busiest mta system in the world
- 23 line in 5 boro, millions rider in NYC
- There are over 500 subway stations, 19 different fare type
- MTA collect fare swipe data for each time rider swipe the card
- MTA release weekly swipe count online

## Dataset:

#### MTA fare Dataset: 
- raw data from MTA website: http://web.mta.info/developers/fare.html
- data frame from New York State Open Data: https://data.ny.gov/Transportation/Fare-Card-History-for-Metropolitan-Transportation-/v7qc-gwpn

- add the snapshot of

## Questions:
- what is the overall trend of fare card usage in MTA system, by Year and Month?
- what are the busiest subway station in MTA, and which fare type are most commently used?
- Any insight information can be extracted form the dataset?
    + There are increased use of Sinior/Disable fare type from 2011 to 2016
    + There are increased use of Mail / Unlimited fare card use
    + 
- what information can be used to improve the service or make more profit
        + for specific group of MTA rider
        + Ad in specific station or fare card

## Shiny App

```{r pressure, echo=FALSE}
shiny::shinyAppDir(
    appDir = "/Users/wanggene/GitHub/MTA/",
  # system.file("/Users/wanggene/GitHub/MTA/", package="shiny"),
    options=list(
     width="120%", height=600
  )
)

```

## Summary

- Use Shiny App, we can have a overview of MTA fare history dataset
- We 
- 

## Future Works

- Add the proportion information in the plot, and do statistic analysis.
- Integate geographic information into app, we can observe the change.
- Keep update with MTA website, add new data in the data frame.

##                          Thank You!

